\documentclass{ExpressiveResume}

% ============= PACKAGES ==============

\usepackage{hyperref}

% ============= PACKAGES ==============

\begin{document}

% You will write your resume here.

\resumeheader[
    firstname=Branden,             % Your first name
    lastname=Kim,              % Your last name
    email=brandenkiminq@gmail.com,                 % Your email
    phone=703-223-1009,                 % Your phone number, formatted as XXX-XXX-XXXX
    linkedin=branden-kim-17704513b,              % Your LinkedIn handle (without the @)
    github=psiionik,                % Your GitHub handle (without the @)
    city=Fairfax,                  % Your city of residence (ignored if no `state` is given)
    state=,                 % Your state of residence
    qrcode=./images/qr.png,                % the path to a qr code to show in the top right corner
]

\objective{
    Senior Software Engineer with 5 years of experience, pursuing a
    masters degree in ML part-time seeking opportunities to develop
    data pipelines for ML infrastructure.
}

% \summary{
%     % Write your summary statement here.
% }

% ----- Work Experience -----
\section{Work Experience}

\experience{Sonos}{
    \role{Senior Software Engineer}{Aug 2020  - Feb 2025}{
        \achievement{
            Designed and implemented a distributed Update Server that aggregates
            update information from products and delivers firmware and software
            updates to 50 million products worldwide.
            \begin{itemize}
                \item Designed and implemented a distributed Content
                      Delivery Network to optimize update times and gathering
                      of product data in data streams using geolocation.

                \item Performed performance optimization on latency and
                      CPU utilization by utilizing Jenkins and K8s to
                      spin up millions of requests. Improved latency by
                      300\% and reduced CPU \% utilization through
                      orchestrating a Horizontal Pod Autoscaler in
                      kubernetes.

                \item Designed and implemented a Redis Caching Layer to
                      reduce read requests on our RDB cluster by 92\%.

                \item Implemented a static caching layer to re-direct
                      88\% of requests from the origin to edge location servers.

                \item Analyzed sql query plans and DB locking mechanisms
                      and indexes to optimize READ performance on the DB
                      Cluster.

                \item Implemented an automated CI / CD pipeline
                      utilizing Jenkins and Github Actions to automate
                      blue-green deployments and preventing bugs through
                      automating our testing framework.

                \item Analyzed network traffic through our logging
                      pipeline and implemented a data streaming pipeline using
                      S3 and Kinesis to store 3 million users and 50 million
                      product information in a data lake for analysis.
            \end{itemize}
        }
        \achievement{
            Designed and implemented a functional style, data-model driven
            PostgresSQL internal library utilized in a 3-tier service that
            centralized meta-information about products, firmware, and
            releases.

            \begin{itemize}
                \item Implemented an exhaustive type system that allows
                      for composition of custom multiple sql commands across data
                      models in DB transaction-chains in a declarative
                      style.
                \item Centralized all meta-information that allowed
                      developers to look-up and create update packages for
                      testing and release.
                \item Improved build-to-release times from 6 hours down
                      to 2 hours.
                \item Allowed efficient searching of multiple products
                      based on shared query properties that allows for efficient auditing.
            \end{itemize}
        }
        \achievement{
            Designed and implemented a virtual pipeline framework in Scala
            to create a custom, automated CI / CD pipeline tool that
            utilized Jenkins in its backend to automate the queuing of jobs
            to build, deliver, and release firmware across all products.
            \begin{itemize}
                \item Converted a manual release process into an
                      automated release process that allows releases of
                      firmware of all products to Alpha, Beta, Production
                      users.
                \item Reduced developer bugs and Jenkins plugin issues
                      by 72\% by creating a virtualization of Jenkins jobs that allows
                      developers to declaratively specify their job using
                      Scala classes and config files.
                      % \item Implemented bunch of python scripts that were
                      %       called by the virtualization process to automate release
                      %       of firmware / software to different destinations, App
                      %       Stores, Update Server, Development Environments, etc.
            \end{itemize}
        }
    }
    \role{Software Engineer}{Aug 2020 - Nov 2023}{
        \achievement{
            Implemented an internal fullstack, microservices app on AWS Lambda, S3, and
            StepFunctions for CRUD operations on internal user, product, user
            groups, and update records integrating Okta with SAML authentication
            to authenticate privileged users.
            \begin{itemize}
                \item Implemented automated CI / CD pipeline utilizing
                      Jenkins and Github Actions with a Gitflow workflow
                      branching strategy to allow for parallel development
                      and streamline the rollout of features and bug-fixes.
                \item Provided distributed load-balancing and SSL
                      termination by deploying a custom NGINX web-server in
                      front of AWS Lambda microservices.
                \item Implemented a custom MapReduce framework library
                      utilizing S3 and StepFunctions in order to process
                      updates to batches of millions of users at once.
                \item Utilized the Serverless framework to declaratively
                      create infrastructure and DAO design pattern with custom
                      SQL stored procedures to perform DB calls.
                \item Implemented an expansion to the app's features by
                      implementing updates to Redis Caches and other service's
                      DBs upon updates to internal data.
            \end{itemize}
        }

        \achievement{
            Designed and implemented a metrics and log aggregation stream
            by utilizing a Prometheus and Loki server hosted on Kubernetes
            sidecars to aggregate metrics and logs from automation jobs running
            on Jenkins.
            \begin{itemize}
                \item Led to aggregation of job metrics and logs that allowed
                      for optimization of build bottlenecks and reduced bugs
                      by 12\%.
                \item Scaled by deploying these services to a Kubernetes
                      cluster as a sidecar to existing pod services.
            \end{itemize}
        }

        \achievement{
            Designed and implemented automation to building and release
            delivery of product firmware and meta-data by creating
            custom workflow scripts in python and Jenkins for job infrastructure.
            \begin{itemize}
                \item Optimized the job's completion time from 12
                      minutes to 1.5 minutes by utilizing
                      multiprocessing.
                \item Automated existing manual processes such as
                      utilizing rsync to copy files to file-stores and servers
                      for distribution.
            \end{itemize}
        }
    }
}

\experience{University of Virginia}{
    \role{Research Assistant}{Aug 2019  - Aug 2020}{

    }
    \role{Data Structures and Algorithms Teaching Assistant}{Jan 2019 -
        Aug 2020} {

    }
}

% ----- Projects -----
\section{Technical Projects}

\project{scwab}{2025}{
    \achievement{
        Implemented a compiler from scratch for the wabbit programming
        language using Scala and a data-model driven functional
        programming style.
    }
}

\project{Transformer-Based Electronic Sub-Genre Classifier}{2025}{
    \achievement{
        Wrote a research paper on implementing a custom Transformer based
        model architecture for multi-genre music classification specifically
        in sub-genres in electronic music. Performed transfer learning to
        utilize an existing BERT model and re-trained on the FMA music
        dataset and again on a custom dataset with only electronic music.
        Utilized Fourier Transforms to create embeddings of 30 second music
        samples which led to a 77\% Sensitivity and 78\% Specificity rate.
    }
}

\project{CG Raytracer}{2025}{
    \achievement{
        Implemented a 3D RayTracer in Java for fun / learning purposes
        utilizing the Processing library in Java. Implemented
        ray-generation, phong lighting models, shape collision algorithms,
        and BVH Trees for optimization.
    }
}

% ----- Education -----
\section{Education}

\degree{M.S Computer Science ML Specialization}{Georgia Institute
    of Technology}{2021 - Present}{
}

\degree{B.S Computer Science \honors{Summa Cum Laude}}{University of
    Virginia}{2016 - 2020}{
    % Extra information, e.g. \achievement's
}

\degree{Bradfield School of Computer Science}{Certifcation of Completion}{2022 - 2023}{
    \achievement{
        Year long private institution program that aimed at breaking
        software abstractions by understanding low-level software
        abstractions and building up to implementing distributed consensus
        algorithms like raft.
    }
}

% ----- Certifications -----
\section{Certifications / Courses}

\tech{NVIDIA Deep Learning Fundamentals} |
\tech{Architecting on AWS} |
\tech{Advanced Architecting on AWS}

% ----- Tools / Skills -----
\section{Skills}

\tech{Python}
\tech{Pytorch}
\tech{Java}
\tech{Go}
\tech{Docker}
\tech{Terraform}
\tech{Kubernetes}
\tech{Redis}
\tech{Scala}
\tech{Typescript}
\tech{JavaScript}
\tech{C}
\tech{C++}
\tech{AWS}
\tech{Serverless}

\end{document}