\documentclass{ExpressiveResume}

% ============= PACKAGES ==============

\usepackage{hyperref}

% ============= PACKAGES ==============

\begin{document}

% You will write your resume here.

\resumeheader[
    firstname=Branden,             % Your first name
    lastname=Kim,              % Your last name
    email=brandenkiminq@gmail.com,                 % Your email
    phone=703-223-1009,                 % Your phone number, formatted as XXX-XXX-XXXX
    linkedin=branden-kim-17704513b,              % Your LinkedIn handle (without the @)
    github=psiionik,                % Your GitHub handle (without the @)
    city=Fairfax,                  % Your city of residence (ignored if no `state` is given)
    state=,                 % Your state of residence
    qrcode=./images/qr.png,                % the path to a qr code to show in the top right corner
]

% ----- Work Experience -----
\section{Work Experience}

\experience{Sonos}{
    \role{Senior Software Engineer}{Oct 2023  - Feb 2025}{
        \achievement{
            Worked on the creation of a world-class build and release delivery
            pipeline to automate and optimize the delivery of high-quality
            firmware to 50 million speakers around the world.
            \begin{itemize}
                \item Optimized storage of firmware assets and
                      reduced time to release by 80\%.
            \end{itemize}
        }
        \achievement{
            Designed and implemented a distributed Update Server that aggregates
            update information from products and delivers firmware and software
            updates to 50 million products worldwide, reducing costs from
            \$700,000 to \$10,000.
            \begin{itemize}
                \item Improved latency by 300\% and reduced CPU utilization through
                      using Kubernetes.

                \item Implemented a Redis Caching Layer, reducing RDB read requests by 92\%.

                \item Created static caching layer to re-direct
                      88\% of requests to edge location servers.
            \end{itemize}
        }
        \achievement{
            Designed and implemented a functional style, data-model driven
            PostgresSQL internal library utilized in a 3-tier service that
            centralized meta-information about products, firmware, and
            releases.
            \begin{itemize}
                \item Implemented an exhaustive type system
                      for declarative composition of custom sql
                      command in virtual DB transaction-chains.

                \item Improved build-to-release times from 6 hours down
                      to 2 hours.
            \end{itemize}
        }
        \achievement{
            Designed and implemented a virtual pipeline framework in Scala
            to create a custom, automated CI / CD pipeline tool that
            utilized Jenkins in its backend to automate the queuing of jobs
            to build, deliver, and release firmware across all products.
            \begin{itemize}
                \item Utilized framework to generate automated release process to release Alpha, Beta, Production
                      firmware.

                \item Virtualized Jenkins jobs to reduce developer bugs
                      and Jenkins plugin issues by 72\%.
            \end{itemize}
        }
    }
    \role{Software Engineer}{Aug 2020 - Oct 2023}{
        \achievement{
            Implemented an internal fullstack, microservices app on AWS Lambda, S3, and
            StepFunctions for CRUD operations on internal user, product, user
            groups, and update records.
            \begin{itemize}
                \item Developed custom MapReduce framework library
                      utilizing S3 and StepFunctions to batch process
                      updates to millions of users.
            \end{itemize}
        }

        \achievement{
            Designed and implemented a metrics and log aggregation stream
            by utilizing a Prometheus and Loki server hosted as a
            sidecar on Kubernetes to aggregate metrics and logs from
            automation jobs running
            on Jenkins.
            \begin{itemize}
                \item Aggregation Jenkins job metrics and logs that
                      optimized build bottlenecks and reduced bugs
                      by 12\%.
            \end{itemize}
        }

        \achievement{
            Designed automation of building and release
            delivery of product firmware and meta-data by creating
            custom workflow scripts in python and Jenkins for job infrastructure.
            \begin{itemize}
                \item Optimized the job's completion time from 12
                      minutes to 1.5 minutes by utilizing
                      multiprocessing.
            \end{itemize}
        }
    }
}

\experience{University of Virginia}{
    \role{Research Assistant}{Aug 2019  - Aug 2020}{

    }
    \role{Data Structures and Algorithms Teaching Assistant}{Jan 2019 -
        Aug 2020} {

    }
}

% ----- Projects -----
\section{Technical Projects}

\project{scwab}{2025}{
    \achievement{
        Implemented a compiler from scratch for the wabbit programming
        language using Scala and a data-model driven functional
        programming style.
    }
}

\project{Transformer-Based Electronic Sub-Genre Classifier}{2025}{
    \achievement{
        Wrote a research paper on implementing a custom Transformer based
        model architecture for multi-genre music classification specifically
        in sub-genres in electronic music. Performed transfer learning to
        utilize an existing BERT model and re-trained on the FMA music
        dataset and again on a custom dataset with only electronic music.
        Utilized Fourier Transforms to create embeddings of 30 second music
        samples which led to a 77\% Sensitivity and 78\% Specificity rate.
    }
}

\project{CG Raytracer}{2025}{
    \achievement{
        Implemented a 3D RayTracer in Java for fun / learning purposes
        utilizing the Processing library in Java. Implemented
        ray-generation, phong lighting models, shape collision algorithms,
        and BVH Trees for optimization.
    }
}

% ----- Education -----
\section{Education}

\degree{M.S Computer Science ML Specialization}{Georgia Institute
    of Technology}{2021 - Present}{
}

\degree{B.S Computer Science \honors{Summa Cum Laude}}{University of
    Virginia}{2016 - 2020}{
    % Extra information, e.g. \achievement's
}

\degree{Bradfield School of Computer Science}{Certifcation of Completion}{2022 - 2023}{
    \achievement{
        Year long private institution program that aimed at breaking
        software abstractions by understanding low-level software
        abstractions and building up to implementing distributed consensus
        algorithms like raft.
    }
}

% ----- Certifications -----
\section{Certifications / Courses}

\tech{NVIDIA AI Anomaly Detection} |
\tech{NVIDIA Deep Learning Fundamentals} |
\tech{Architecting on AWS} |
\tech{Advanced Architecting on AWS}

% ----- Tools / Skills -----
\section{Skills}

\tech{Python}
\tech{Pytorch}
\tech{Java}
\tech{Go}
\tech{Docker}
\tech{Terraform}
\tech{Kubernetes}
\tech{Redis}
\tech{Scala}
\tech{Typescript}
\tech{JavaScript}
\tech{C}
\tech{C++}
\tech{AWS}
\tech{Serverless}

\end{document}